    \documentclass[runningheads]{llncs}
    
    % ---------------------------------------------------------------
    % Include basic ECCV package
  
    % TODO REVIEW: Insert your submission number below by replacing '*****'
    % TODO FINAL: Comment out the following line for the camera-ready version
    \usepackage{microtype}
    \usepackage[review,year=2026,ID=3192]{eccv}
    % TODO FINAL: Un-comment the following line for the camera-ready version
    %\usepackage{eccv}
    
    % OPTIONAL: Un-comment the following line for a version which is easier to read
    % on small portrait-orientation screens (e.g., mobile phones, or beside other windows)
    %\usepackage[mobile]{eccv}
    \usepackage{multirow}
    \usepackage[table]{xcolor}
    \usepackage{appendix}
    \usepackage{amssymb}       % 符号支持
    \usepackage{pifont}
    \usepackage{makecell} % 用于单元格换行

    \usepackage{adjustbox} % 用于精细控制
    \usepackage{caption}

 
    % ---------------------------------------------------------------
    % Other packages
    
    % Commonly used abbreviations (\eg, \ie, \etc, \cf, \etal, etc.)
    \usepackage{eccvabbrv}
    
    % Include other packages here, before hyperref.
    \usepackage{graphicx}
    \usepackage{booktabs}
    
    % The "axessiblity" package can be found at: https://ctan.org/pkg/axessibility?lang=en
    \usepackage[accsupp]{axessibility}  % Improves PDF readability for those with disabilities.
    
    
    % ---------------------------------------------------------------
    % Hyperref package
    
    % It is strongly recommended to use hyperref, especially for the review version.
    % Please disable hyperref *only* if you encounter grave issues.
    % hyperref with option pagebackref eases the reviewers' job, but should be disabled for the final version.
    %
    % If you comment hyperref and then uncomment it, you should delete
    % main.aux before re-running LaTeX.
    % (Or just hit 'q' on the first LaTeX run, let it finish, and you
    %  should be clear).
    
    % TODO FINAL: Comment out the following line for the camera-ready version
    %\usepackage[pagebackref,breaklinks,colorlinks,citecolor=eccvblue]{hyperref}
    % TODO FINAL: Un-comment the following line for the camera-ready version
    \usepackage{hyperref}
    \usepackage{wrapfig}
    % Support for ORCID icon
    \usepackage{orcidlink}
    % 美化
    \usepackage{xcolor}
    \usepackage{pifont}

    \definecolor{firstpurple}{RGB}{240, 235, 255}  % 第一名
    \definecolor{secondpurple}{RGB}{248, 245, 255} % 第二名
    % 定义带颜色的勾和叉
    \newcommand{\cmark}{\textcolor{blue}{\ding{51}}}
    \newcommand{\xmark}{\textcolor{red}{\ding{55}}}
    
    \begin{document}
    
    % ---------------------------------------------------------------
    \title{RoboStream: Weaving \underline{S}patio-\underline{T}emporal \underline{Rea}soning with \underline{M}emory 
    in Vision-Language Models for \underline{Robo}tics}
    
    % TODO REVIEW: If the paper title is too long for the running head, you can set
    % an abbreviated paper title here. If not, comment out.
    \titlerunning{RoboStream}
    
    % TODO FINAL: Replace with your author list. 
    % Include the authors' OCRID for the camera-ready version, if at all possible.
    \author{First Author\inst{1}\orcidlink{0000-1111-2222-3333} \and
    Second Author\inst{2,3}\orcidlink{1111-2222-3333-4444} \and
    Third Author\inst{3}\orcidlink{2222--3333-4444-5555}}
    
    % TODO FINAL: Replace with an abbreviated list of authors.
    \authorrunning{F.~Author et al.}
    % First names are abbreviated in the running head.
    % If there are more than two authors, 'et al.' is used.
    
    % TODO FINAL: Replace with your institution list.
    \institute{Princeton University, Princeton NJ 08544, USA \and
    Springer Heidelberg, Tiergartenstr.~17, 69121 Heidelberg, Germany
    \email{lncs@springer.com}\\
    \url{http://www.springer.com/gp/computer-science/lncs} \and
    ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
    \email{\{abc,lncs\}@uni-heidelberg.de}}
    
    \maketitle
    


\begin{abstract}
Enabling reliable long-horizon robotic manipulation is a crucial step toward open-world embodied intelligence. However, VLM-based planners treat each step as an isolated observation-to-action mapping, forcing them to reinfer scene geometry from raw pixels at every decision step while remaining unaware of how prior actions have reshaped the environment. Despite strong short-horizon performance, these systems lack the spatio-temporal reasoning required for persistent geometric anchoring and memory of action-triggered state transitions. Without persistent state tracking, perceptual errors accumulate across the execution horizon, temporarily occluded objects are catastrophically forgotten, and these compounding failures lead to precondition violations that cascade through subsequent steps. In contrast, humans maintain a persistent mental model that continuously tracks spatial relations and action consequences across interactions rather than reconstructing them at each instant.
Inspired by this human capacity for causal spatio-temporal reasoning with persistent memory, we propose \textbf{RoboStream}, a training-free framework that achieves geometric anchoring through Spatio-Temporal Fusion Tokens (STF-Tokens), which bind visual evidence to 3D geometric attributes for persistent object grounding, and maintains causal continuity via a Causal Spatio-Temporal Graph (CSTG) that records action-triggered state transitions across steps. This design enables the planner to trace causal chains and preserve object permanence under occlusion without additional training or fine-tuning. RoboStream achieves 90.5\% on long-horizon RLBench and 44.4\% on challenging real-world block-building tasks, where both SoFar and VoxPoser score 11.1\%, demonstrating that spatio-temporal reasoning and causal memory are critical missing components for reliable long-horizon manipulation.








\keywords{Robot Manipulation \and Vision-Language Models \and Long-Horizon Planning \and Spatio-Temporal Reasoning \and Causal Memory}
\end{abstract}
    

% \input{Introduction}
% \input{Related_work}
% \input{Method}
% \input{Experiments}
% \vspace{-1em}
% \input{Conclusion}
% \input{Limitation}

% \clearpage
% \bibliographystyle{splncs04}
% \bibliography{main}


\clearpage
\appendix
\input{Appendix}


\end{document}